---
title: "analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DEoptim)
results_path = "results/"
```

# Fit the model to the data

```{r cache=TRUE}
z = source("codes/helpers.R")
z2 = source("codes/PAWN.R")

ndat = 2; # Number of datasets
AICe = seq(1, ndat); AICb = seq(1, ndat);  # Uncorrected AICs
AICce = seq(1, ndat); AICcb = seq(1, ndat);  # AIC with small sample correction
expdev = seq(1, ndat); betadev = seq(1, ndat);  # Minimum deviances of the models
# The best parameters for the fitted models
bestr = seq(1, ndat); bestalpha = seq(1, ndat); bestbeta = seq(1, ndat);
# Optionally store the p_values of the fit (comment out llines with p_beta and p_exp)
# p_exp = seq(1, ndat); p_beta = seq(1, ndat);
mu_exp = seq(1, ndat);  # Calculate mu for the exponential model
set.seed(0)
for (ind in seq(ndat)){
  ds = getdat(ind)  # Get and store the dataset
  solexp = DEoptim(exp_deviance, parameter_list=ds, -12, -5, DEoptim.control(trace = 50));  # Fit the exponential solution
  solbeta = DEoptim(betap_deviance, parameter_list=ds, c(-12,-12), c(50, 50), DEoptim.control(trace = 50));  # Fit the beta Poisson model
  Ke=1; Kb = 2;  # Number of parameters in exp and beta P models
  # Compute the uncorrected AICs
  AICe[ind] = solexp$optim$bestval + 2*Ke;
  AICb[ind] = solbeta$optim$bestval + 2*Kb;
  n = ds$N; # The number of data points
  # Compute the AICs with small sample correction
  AICce[ind] = AICe[ind] + 2*Ke*(Ke+1)/(n-Ke-1)
  AICcb[ind] = AICb[ind] + 2*Kb*(Kb+1)/(n-Kb-1)
  # Store the remaining parameters
  expdev[ind] = solexp$optim$bestval
  betadev[ind] = solbeta$optim$bestval
  bestr[ind] = 10^solexp$optim$bestmem
  bestalpha[ind] = 10^solbeta$optim$bestmem[1]
  bestbeta[ind] = 10^solbeta$optim$bestmem[2]
  mu_exp[ind] = -1/ds$t * log1mexpm(bestr[ind])
  # p_exp[ind] = 1 - pchisq(expdev[ind],n-1)
  # p_beta[ind] = 1 - pchisq(betadev[ind],n-2)
}

# Store the important columns in a data frame
results = data.frame(expdev = expdev, betadev = betadev, 
                     # pexp = p_exp, pbeta = p_beta,
                     # AIC_exp = AICe, AIC_beta = AICb,
                     AICc_exp = AICce, AICc_beta = AICcb,
                     r = bestr,
                     alpha = bestalpha, beta = bestbeta,
                     mu_r = mu_exp,
                     # mod = ifelse(p_exp<0.05, "beta", "exp")
                     mod = ifelse(AICcb<AICce, "beta", "exp"))
results
# Save the results
save(results, file=paste(results_path, "fit.Rda", sep=""))
```

# Create data frames to make the effect plot

```{r cache=TRUE}
# Make the relevant data frames
top = get_plot_dataframes(1, results);
bottom = get_plot_dataframes(2, results);
save(top, bottom, file=paste(results_path, "effect.Rda", sep=""))
```

# Sensitivity analysis

Define some parameters.
```{r}

# PAWN parameters (main ones)

n=15;
Nu = 100;
Nc = 100;
# Critical value pre-multipliers
crit_c = c(1.22,1.36,1.48,1.63,1.73,1.95); # 0.1, 0.05, 0.025, 0.010, 0.005, 0.001
# Actual critical value based on significance level
critval = crit_c[2] * sqrt((Nu+Nc)/(Nu*Nc))


# PAWN parameters (auxiliary ones)
npts = 100; seed = 0;

r = 1.066597e-08; # Dataset 1, best fit
alpha = 1.623144e-01; beta = 1.414959e+06; # Dataset 2, best fit
Emax =  1224; Ec50 = 9.93; # Antibiotic specifcic parameters

# Sensitivity analysis bounds related parameters
doselb = 1; doseub = 4;
factor = 0.5; # Factor of change for Emax, Ec50, alpha and beta.
```

## Sensitivity at variable dose

### Exponential model
```{r}
# Bounds
lb = c(0.00, 0.0, doselb, Emax-factor*Emax, Ec50-factor*Ec50, r-factor*r, 1.5);
ub = c(0.05, 0.1, doseub, Emax+factor*Emax, Ec50+factor*Ec50, r+factor*r, 2.5);
p = getdat(1)  # retrieve dataset
res_exp = PAWN(get_exprisk, p, lb, ub, Nu, n, Nc, npts, seed, 4)  # run sensitivity analysis
```

### Beta Poisson model
```{r}
# Bounds
lb = c(0.00, 0.0, doselb, Emax-factor*Emax, Ec50-factor*Ec50, alpha-factor*alpha, beta-factor*beta, 2);
ub = c(0.05, 0.1, doseub, Emax+factor*Emax, Ec50+factor*Ec50, alpha+factor*alpha, beta+factor*beta, 3);
p = getdat(2)
res_beta = PAWN(get_bprisk, p, lb, ub, Nu, n, Nc, npts, seed, 4)  # run sensitivity analysis
```

## Sensitivity at fixed dose

Fix the dose and perform sensitivity analysis. Changing the value at which the dose is fixed does not change the output very much.
```{r}
dval = 1e4;
```

### Exponential model

```{r}
# Bounds
lb = c(0.00, 0.0, Emax-factor*Emax, Ec50-factor*Ec50, r-factor*r, 1.5);
ub = c(0.05, 0.1, Emax+factor*Emax, Ec50+factor*Ec50, r+factor*r, 2.5);
p = getdat(1); p$dose = dval;  # get the data and set the dose
resnd_exp = PAWN(get_exprisk_nodose, p, lb, ub, Nu, n, Nc, npts, seed, 4) # run sensitivity analysis
```

### Beta Poisson model

```{r}
# Bounds
lb = c(0.00, 0.0, Emax-factor*Emax, Ec50-factor*Ec50, alpha-factor*alpha, beta-factor*beta, 2);
ub = c(0.05, 0.1, Emax+factor*Emax, Ec50+factor*Ec50, alpha+factor*alpha, beta+factor*beta, 3);
p = getdat(2); p$dose = dval;  # get the data and set the dose
resnd_beta = PAWN(get_bprisk_nodose, p, lb, ub, Nu, n, Nc, npts, seed, 2)
```

```{r}
save(res_exp, resnd_exp, res_beta, resnd_beta, n, critval, Nu, Nc, file=paste(results_path, "sens.Rda", sep=""))
```

# Verify beta procedure

```{r}
b_res = get_beta_verification(2, results);
save(b_res, file=paste(results_path, "betaver.Rda", sep=""))
```